Supporting Information

### 2018-03-12 SupportingInformation.Rmd
minor additional edits

The difference $\cor_l-\cor_u$ is expected to be positive if 
dependence in the left halves of the distributions is stronger 
than dependence in their right halves; likewise for $\P_l-\P_u$.
This holds, for instance, for the Clayton copula (REF).
<!--Shya to cite the Nelson book-->
On the other hand, the difference $\D2_u-\D2_l$ is expected to be 
positive under the same conditions, so we use these three differences
to detect asymmetry of tail dependence.

>>>>

The difference $\cor_l-\cor_u$ is expected to be positive if 
dependence in the left halves of the distributions is stronger 
than dependence in their right halves; likewise for $\P_l-\P_u$.
This holds, for instance, for the Clayton copula (REF).
<!--Shya to cite the Nelson book-->
The difference $\D2_u-\D2_l$, in which the "upper" and
"lower" statistics occur in opposite order, is also expected to be 
positive under the same conditions. We use these three differences
to detect asymmetry of tail dependence. Likewise, for large datasets,
we consider $\cor_{l_b,u_b}-\cor_{1-u_b,1-l_b}$, 
$\P_{l_b,u_b}-\P_{1-u_b,1-l_b}$ and
$\D2_{1-u_b,1-l_b}-\D2_{l_b,u_b}$ with $l_b=0$ and $u_b$ close to $0$.
